Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-10-25 Methods-and-Results.Rmd
AOT-P contact H. conclusion added

We additionally used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants. We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (\textit{b} = `r coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","Value"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmeInterceptAttType$fixDF$X["OutgroupInteractionYes"] %>% as.numeric`) = `r coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","t-value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} `r ifelse(coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","p-value"]<.001, "< .001", paste0("= ", coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","p-value"] %>% round(3) %>% format(nsmall=3)))`, \textit{95\%CI}[`r mdlWorker$lmerInterceptAttTypeCI["OutgroupInteractionYes", "2.5 %"]`, `r mdlWorker$lmerInterceptAttTypeCI["OutgroupInteractionYes", "97.5 %"]`]), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Online Supplementary Materials B).

>>>>

We additionally used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants. We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (\textit{b} = `r coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","Value"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmeInterceptAttType$fixDF$X["OutgroupInteractionYes"] %>% as.numeric`) = `r coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","t-value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} `r ifelse(coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","p-value"]<.001, "< .001", paste0("= ", coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","p-value"] %>% round(3) %>% format(nsmall=3)))`, \textit{95\%CI}[`r mdlWorker$lmerInterceptAttTypeCI["OutgroupInteractionYes", "2.5 %"] %>% round(2) %>% format(nsmall=2)`, `r mdlWorker$lmerInterceptAttTypeCI["OutgroupInteractionYes", "97.5 %"] %>% round(2) %>% format(nsmall=2)`]), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Online Supplementary Materials B). Thus, in our first data we find mixed results, where outgroup contacts show a positive effect on outgroup attitudes in the moment but these results do not translate into average differences between participants, keeping in mind that the between-participant effects in the aggregated form are based in a small sample size.

### 2021-10-25 Methods-and-Results.tex
AOT-P contact H. conclusion added

We additionally used a multilevel regression to check whether having an
interaction with an outgroup member had a situational (i.e.,
contemporaneous) effect within the participants. We find that having an
outgroup interaction is indeed associated with significantly more
positive outgroup attitudes within the participants (\textit{b} = 2.48,
\textit{t}(1200) = 4.36, \textit{p} \textless{} .001,
\textit{95\%CI}{[}1.3644, 3.5884{]}), even after controlling for having
an interaction with a non-Dutch (which did not relate to outgroup
attitudes independently; For full results see Online Supplementary
Materials B).

>>>>

We additionally used a multilevel regression to check whether having an
interaction with an outgroup member had a situational (i.e.,
contemporaneous) effect within the participants. We find that having an
outgroup interaction is indeed associated with significantly more
positive outgroup attitudes within the participants (\textit{b} = 2.48,
\textit{t}(1200) = 4.36, \textit{p} \textless{} .001,
\textit{95\%CI}{[}1.36, 3.59{]}), even after controlling for having an
interaction with a non-Dutch (which did not relate to outgroup attitudes
independently; For full results see Online Supplementary Materials B).
Thus, in our first data we find mixed results, where outgroup contacts
show a positive effect on outgroup attitudes in the moment but these
results do not translate into average differences between participants,
keeping in mind that the between-participant effects in the aggregated
form are based in a small sample size.
